Quantile Trend Filtering via Spingarn's Method

### 2017-05-30 Notes/detrendify_spingarn.tex
Some small edits to the document.

\begin{eqnarray*}
\V{x}^+ & = & \prox{t\psi}{\V{z}} \\
\V{y}^+ & = & P_V(2\V{x}^+ - \V{z}) \\
\V{z}^+ & = & \V{z} + \V{y}^+ - \V{x}^+.
\end{eqnarray*}
The parameter $t$ is a step-size which can be fixed at 1 to guarantee convergence. The mapping $P_V$ is the orthogonal projection onto the set $V$.

@@

\begin{itemize}
\item The overall computational complexity is essentially linear $\mathcal{O}(nk^2)$ for the initial banded Cholesky decomposition and the per-iteration complexity is $\mathcal{O}(nk)$.
\item One could also apply Anderson acceleration to reduce the number of Spingarin updates, since the Douglas-Rachford algorithm is a fixed point algorithm.
\end{itemize}

>>>>

\begin{eqnarray*}
\V{x}^+ & = & \prox{t\psi}{\V{z}} \\
\V{y}^+ & = & P_V(2\V{x}^+ - \V{z}) \\
\V{z}^+ & = & \V{z} + \lambda(\V{y}^+ - \V{x}^+).
\end{eqnarray*}
The parameter $t$ is a step-size and $\lambda_n$ is Karolinski-Mann. We require that $\lambda_n \in ]0, 2[$ and that $\sum_n \lambda_n(1-\lambda_n) = \infty$. The mapping $P_V$ is the orthogonal projection onto the set $V$.

@@

\begin{itemize}
\item The overall computational complexity is essentially linear $\mathcal{O}(nk^2)$ for the initial banded Cholesky decomposition and the per-iteration complexity is $\mathcal{O}(nk)$.
\item One could also apply Anderson acceleration to reduce the number of Spingarn updates, since the Douglas-Rachford algorithm is a fixed point algorithm.
\end{itemize}
